---
title: "Buttons"
subtitle: "Interactive button components with OEDA branding"
format: html
---

# Button Components

This page demonstrates how to implement consistent button styling across your projects using OEDA brand colors and design patterns.

## Primary Buttons

Use primary buttons for the main action on a page or section.

```{r primary-buttons}
#| echo: false
#| output: asis

cat('<div class="demo-section">
<h3>Live Example</h3>
<button type="button" class="btn btn-primary">Primary Action</button>
<button type="button" class="btn btn-primary" disabled>Disabled Primary</button>
</div>')

```

### HTML Code
```html
<button type="button" class="btn btn-primary">Primary Action</button>
<button type="button" class="btn btn-primary" disabled>Disabled Primary</button>
```

### CSS (Add to your theme.scss file)
```css
/*-- scss:rules --*/

.btn-primary {
  background-color: var(--bs-primary);
  border-color: var(--bs-primary);
  color: white;
}

.btn-primary:hover {
  background-color: var(--bs-secondary);
  border-color: var(--bs-secondary);
}

.btn-primary:disabled {
  opacity: 0.6;
  cursor: not-allowed;
}
```

## Secondary Buttons

Use secondary buttons for supporting actions or when you need multiple buttons in close proximity.

```{r secondary-buttons}
#| echo: false
#| output: asis


cat('<div class="demo-section">
<h3>Live Example</h3>
<button type="button" class="btn btn-secondary">Secondary Action</button>
<button type="button" class="btn btn-outline-primary">Outlined Button</button>
</div>')


```

### HTML Code
```html
<button type="button" class="btn btn-secondary">Secondary Action</button>
<button type="button" class="btn btn-outline-primary">Outlined Button</button>
```

## Button Sizes

Different button sizes for various contexts.

```{r button-sizes}
#| echo: false
#| output: asis


cat('<div class="demo-section">
<h3>Live Example</h3>
<button type="button" class="btn btn-primary btn-lg">Large Button</button>
<button type="button" class="btn btn-primary">Regular Button</button>
<button type="button" class="btn btn-primary btn-sm">Small Button</button>
</div>')

```

### HTML Code
```html
<button type="button" class="btn btn-primary btn-lg">Large Button</button>
<button type="button" class="btn btn-primary">Regular Button</button>
<button type="button" class="btn btn-primary btn-sm">Small Button</button>
```

## Action Buttons

Specialized buttons for common actions in data analytics contexts.

```{r action-buttons}
#| echo: false
#| output: asis


cat('<div class="demo-section">
<h3>Live Example</h3>
<button type="button" class="btn btn-success">
  <i class="bi bi-download"></i> Download Report
</button>
<button type="button" class="btn btn-info">
  <i class="bi bi-bar-chart"></i> View Chart
</button>
<button type="button" class="btn btn-warning">
  <i class="bi bi-exclamation-triangle"></i> Alert
</button>
<button type="button" class="btn btn-danger">
  <i class="bi bi-trash"></i> Delete
</button>
</div>')

```

### HTML Code
```html
<button type="button" class="btn btn-success">
  <i class="bi bi-download"></i> Download Report
</button>
<button type="button" class="btn btn-info">
  <i class="bi bi-bar-chart"></i> View Chart
</button>
<button type="button" class="btn btn-warning">
  <i class="bi bi-exclamation-triangle"></i> Alert
</button>
<button type="button" class="btn btn-danger">
  <i class="bi bi-trash"></i> Delete
</button>
```

## Button Groups

Group related buttons together for cleaner interfaces.

```{r button-groups}
#| echo: false
#| output: asis


cat('<div class="demo-section">
<h3>Live Example</h3>
<div class="btn-group" role="group" aria-label="Data view options">
  <button type="button" class="btn btn-outline-primary active">Table</button>
  <button type="button" class="btn btn-outline-primary">Chart</button>
  <button type="button" class="btn btn-outline-primary">Export</button>
</div>
</div>')
```

### HTML Code
```html
<div class="btn-group" role="group" aria-label="Data view options">
  <button type="button" class="btn btn-outline-primary active">Table</button>
  <button type="button" class="btn btn-outline-primary">Chart</button>
  <button type="button" class="btn btn-outline-primary">Export</button>
</div>
```

## Usage Guidelines

### When to Use Each Type

- **Primary**: Use for the main action users should take (Submit, Save, Continue)
- **Secondary**: Use for secondary actions (Cancel, Back, Reset)  
- **Outlined**: Use when you need a button that's less prominent than secondary
- **Action buttons**: Use semantic colors for specific actions (Success for downloads, Warning for alerts, etc.)

### Best Practices

- Limit to one primary button per section
- Use consistent spacing between buttons
- Always include descriptive text, not just icons
- Ensure sufficient color contrast for accessibility
- Test button interactions in both light and dark modes

### Accessibility Notes

- All buttons include proper ARIA labels
- Color is not the only way to convey information
- Focus states are clearly visible
- Disabled states are properly indicated to screen readers

## Custom SCSS for theme.scss

Add this to the `/*-- scss:rules --*/` section of your `theme.scss` file:

```scss
/*-- scss:rules --*/

// Custom button styling
.demo-section {
  padding: 1rem;
  border: 1px solid var(--bs-border-color);
  border-radius: 0.375rem;
  margin: 1rem 0;
  background-color: var(--bs-body-bg);
}

.demo-section h3 {
  margin-top: 0;
  margin-bottom: 1rem;
  color: var(--bs-headings-color);
}

// Enhanced button hover effects
.btn {
  transition: all 0.15s ease-in-out;
}

.btn:hover {
  transform: translateY(-1px);
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
}

// Button group spacing
.btn-group .btn {
  margin-right: 0;
}

.btn + .btn {
  margin-left: 0.5rem;
}

.btn-group .btn + .btn {
  margin-left: 0;
}
```