---
title: "Value Box Cards"
subtitle: "Bootstrap cards styled like Quarto Dashboard value boxes for websites"
format:
  html:
    theme:
      light: [flatly, theme.scss]
      dark: [darkly, theme-dark.scss]
---

# Value Box Style Cards

Since Quarto value boxes only work in Dashboard format, this page shows how to create **value box-style components using Bootstrap cards** that work in regular Quarto websites while maintaining the same visual design and functionality.


## Why Use Value Box Style Cards?

These cards replicate the look and feel of Quarto Dashboard value boxes but work in:
- ✅ **Quarto Websites** (like this site)
- ✅ **Regular HTML pages**
- ✅ **R Markdown documents**
- ✅ **Any Bootstrap-based project**

## Basic Value Box Card

<div class="card value-box-card">
  <div class="card-body">
    <div class="value-box-icon">
      <i class="bi bi-currency-dollar"></i>
    </div>
    <div class="value-box-content">
      <div class="value-box-title">Revenue</div>
      <div class="value-box-value">$2.4M</div>
      <div class="value-box-subtitle">Q4 2024 Total</div>
    </div>
  </div>
</div>

```{r basic-value-box}
#| echo: false
#| output: asis

cat('<div class="demo-section">
<h3>Live Example</h3>
<div class="row">
  <div class="col-md-4">
    <div class="card value-box-card">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-currency-dollar"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Revenue</div>
          <div class="value-box-value">$2.4M</div>
          <div class="value-box-subtitle">Q4 2024 Total</div>
        </div>
      </div>
    </div>
  </div>
</div>
</div>')
```

### HTML Code
```html
<div class="card value-box-card">
  <div class="card-body">
    <div class="value-box-icon">
      <i class="bi bi-currency-dollar"></i>
    </div>
    <div class="value-box-content">
      <div class="value-box-title">Revenue</div>
      <div class="value-box-value">$2.4M</div>
      <div class="value-box-subtitle">Q4 2024 Total</div>
    </div>
  </div>
</div>
```

## Value Box Cards with Change Indicators

The key feature your team wanted - showing positive/negative changes with appropriate colors.

```{r change-indicator-cards}
#| echo: false
#| output: asis

cat('<div class="demo-section">
<h3>Live Example</h3>
<div class="row">
  <div class="col-md-4">
    <div class="card value-box-card value-box-success">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-currency-dollar"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Revenue</div>
          <div class="value-box-value">$2.4M</div>
          <div class="value-box-change positive">
            <i class="bi bi-arrow-up"></i> +12.5% vs last quarter
          </div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-md-4">
    <div class="card value-box-card value-box-danger">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-people"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Active Users</div>
          <div class="value-box-value">847</div>
          <div class="value-box-change negative">
            <i class="bi bi-arrow-down"></i> -3.2% vs last week
          </div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-md-4">
    <div class="card value-box-card value-box-info">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-bar-chart"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Conversion Rate</div>
          <div class="value-box-value">4.2%</div>
          <div class="value-box-change neutral">
            <i class="bi bi-dash"></i> No change vs target
          </div>
        </div>
      </div>
    </div>
  </div>
</div>
</div>')
```

### HTML Code
```html
<!-- Positive Change -->
<div class="card value-box-card value-box-success">
  <div class="card-body">
    <div class="value-box-icon">
      <i class="bi bi-currency-dollar"></i>
    </div>
    <div class="value-box-content">
      <div class="value-box-title">Revenue</div>
      <div class="value-box-value">$2.4M</div>
      <div class="value-box-change positive">
        <i class="bi bi-arrow-up"></i> +12.5% vs last quarter
      </div>
    </div>
  </div>
</div>

<!-- Negative Change -->
<div class="card value-box-card value-box-danger">
  <div class="card-body">
    <div class="value-box-icon">
      <i class="bi bi-people"></i>
    </div>
    <div class="value-box-content">
      <div class="value-box-title">Active Users</div>
      <div class="value-box-value">847</div>
      <div class="value-box-change negative">
        <i class="bi bi-arrow-down"></i> -3.2% vs last week
      </div>
    </div>
  </div>
</div>
```

## Color Variants

Different background colors to match the semantic meaning of your metrics.

```{r color-variants}
#| echo: false
#| output: asis

cat('<div class="demo-section">
<h3>Live Example</h3>
<div class="row">
  <div class="col-md-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-primary">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-graph-up"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Growth</div>
          <div class="value-box-value">15.7%</div>
          <div class="value-box-subtitle">Primary Theme</div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-md-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-success">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-check-circle"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Success</div>
          <div class="value-box-value">98.5%</div>
          <div class="value-box-subtitle">Success Theme</div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-md-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-warning">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-exclamation-triangle"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Warnings</div>
          <div class="value-box-value">3</div>
          <div class="value-box-subtitle">Warning Theme</div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-md-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-danger">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-x-circle"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Errors</div>
          <div class="value-box-value">0</div>
          <div class="value-box-subtitle">Danger Theme</div>
        </div>
      </div>
    </div>
  </div>
</div>
</div>')
```

### HTML Code for Color Variants
```html
<!-- Primary (Blue) -->
<div class="card value-box-card value-box-primary">
  <!-- content -->
</div>

<!-- Success (Green) -->
<div class="card value-box-card value-box-success">
  <!-- content -->
</div>

<!-- Warning (Yellow) -->
<div class="card value-box-card value-box-warning">
  <!-- content -->
</div>

<!-- Danger (Red) -->
<div class="card value-box-card value-box-danger">
  <!-- content -->
</div>
```

## Dashboard Layout Example

How to arrange multiple value box cards in a dashboard-style layout.

```{r dashboard-layout}
#| echo: false
#| output: asis

cat('<div class="demo-section">
<h3>Dashboard Layout Example</h3>
<div class="row mb-4">
  <div class="col-sm-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-primary">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-currency-dollar"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Total Revenue</div>
          <div class="value-box-value">$2.4M</div>
          <div class="value-box-change positive">
            <i class="bi bi-arrow-up"></i> +12.5%
          </div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-sm-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-info">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-people"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Active Users</div>
          <div class="value-box-value">1,247</div>
          <div class="value-box-change negative">
            <i class="bi bi-arrow-down"></i> -3.2%
          </div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-sm-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-success">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-graph-up"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Conversion</div>
          <div class="value-box-value">4.2%</div>
          <div class="value-box-change positive">
            <i class="bi bi-arrow-up"></i> +0.8%
          </div>
        </div>
      </div>
    </div>
  </div>
  <div class="col-sm-6 col-lg-3 mb-3">
    <div class="card value-box-card value-box-warning">
      <div class="card-body">
        <div class="value-box-icon">
          <i class="bi bi-clock"></i>
        </div>
        <div class="value-box-content">
          <div class="value-box-title">Response Time</div>
          <div class="value-box-value">124ms</div>
          <div class="value-box-change negative">
            <i class="bi bi-arrow-up"></i> +15ms
          </div>
        </div>
      </div>
    </div>
  </div>
</div>
</div>')
```

## Usage Guidelines

### When to Use Each Color

- **`value-box-primary`** - Main KPIs, revenue, primary metrics
- **`value-box-success`** - Positive trends, goals achieved, systems healthy
- **`value-box-danger`** - Negative trends, errors, alerts, problems
- **`value-box-warning`** - Caution states, approaching limits, maintenance
- **`value-box-info`** - Neutral information, general metrics, informational data

### Change Indicator Best Practices

- **Always include direction**: Use arrows (↑↓) or icons (bi-arrow-up/down)
- **Provide context**: "vs last quarter", "vs target", "vs last week"
- **Use consistent formatting**: Same decimal places, same comparison periods
- **Color coding**: Green for positive, red for negative, gray for neutral

### Layout Recommendations

- **Mobile-first**: Use responsive grid classes (col-sm-6 col-lg-3)
- **Consistent spacing**: Add margin-bottom (mb-3) for proper spacing
- **Group related metrics**: Place similar metrics together
- **Logical order**: Most important metrics first (left to right, top to bottom)

## Add to your theme.scss

Add this comprehensive styling to the `/*-- scss:rules --*/` section of your `theme.scss` file:

```scss
/*-- scss:rules --*/

// =====================================================
// VALUE BOX CARDS
// =====================================================

.value-box-card {
  border: none;
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
  transition: transform 0.2s ease, box-shadow 0.2s ease;
  height: 100%;
}

.value-box-card:hover {
  transform: translateY(-2px);
  box-shadow: 0 4px 12px rgba(0,0,0,0.15);
}

.value-box-card .card-body {
  padding: 1.5rem;
  display: flex;
  align-items: center;
  gap: 1rem;
}

.value-box-icon {
  font-size: 2.5rem;
  opacity: 0.8;
  flex-shrink: 0;
  width: 60px;
  text-align: center;
}

.value-box-content {
  flex: 1;
  min-width: 0;
}

.value-box-title {
  font-size: 0.85rem;
  font-weight: 600;
  text-transform: uppercase;
  letter-spacing: 0.5px;
  opacity: 0.8;
  margin-bottom: 0.25rem;
}

.value-box-value {
  font-size: 1.75rem;
  font-weight: 700;
  line-height: 1.2;
  margin-bottom: 0.25rem;
}

.value-box-subtitle {
  font-size: 0.8rem;
  opacity: 0.7;
  margin: 0;
}

.value-box-change {
  font-size: 0.8rem;
  font-weight: 600;
  margin: 0;
}

.value-box-change.positive {
  color: var(--bs-success);
}

.value-box-change.negative {
  color: var(--bs-danger);
}

.value-box-change.neutral {
  color: var(--bs-secondary);
}

// Color variants
.value-box-primary {
  background: linear-gradient(135deg, var(--bs-primary) 0%, rgba(var(--bs-primary-rgb), 0.8) 100%);
  color: white;
}

.value-box-success {
  background: linear-gradient(135deg, var(--bs-success) 0%, rgba(var(--bs-success-rgb), 0.8) 100%);
  color: white;
}

.value-box-danger {
  background: linear-gradient(135deg, var(--bs-danger) 0%, rgba(var(--bs-danger-rgb), 0.8) 100%);
  color: white;
}

.value-box-warning {
  background: linear-gradient(135deg, var(--bs-warning) 0%, rgba(var(--bs-warning-rgb), 0.8) 100%);
  color: white;
}

.value-box-info {
  background: linear-gradient(135deg, var(--bs-info) 0%, rgba(var(--bs-info-rgb), 0.8) 100%);
  color: white;
}

// Dark mode adjustments
[data-bs-theme="dark"] .value-box-card {
  box-shadow: 0 2px 4px rgba(0,0,0,0.3);
}

[data-bs-theme="dark"] .value-box-card:hover {
  box-shadow: 0 4px 12px rgba(0,0,0,0.4);
}
```

This approach gives you all the visual appeal and functionality of Quarto Dashboard value boxes, but works perfectly in your Quarto website!